---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# DGLMExtPois

<!-- badges: start -->
[![R-CMD-check](https://github.com/franciscomartinezdelrio/DGLMExtPois/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/franciscomartinezdelrio/DGLMExtPois/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

DGLMExtPois is a package that contains statistical functions for the model
estimation, dispersion testing and diagnosis of hyper-Poisson and
Conway-Maxwell-Poisson regression models.

## Installation

You can install the released version of DGLMExtPois from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("DGLMExtPois")
```

and the development version from github with:

```{r gh-installation, eval = FALSE}
devtools::install_github("franciscomartinezdelrio/DGLMExtPois")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example hP}
library(DGLMExtPois)
library(Ecdat)
Bids$size.sq <- Bids$size ^ 2
hP.bids <- glm.hP(formula.mu = numbids ~ leglrest + rearest + finrest +
                    whtknght + bidprem + insthold + size + size.sq +
                    regulatn,
                    formula.gamma = numbids ~ 1,
                    data = Bids)
summary(hP.bids)
AIC(hP.bids)
BIC(hP.bids)
coef(hP.bids)
confint(hP.bids)
head(fitted(hP.bids))
head(residuals(hP.bids))
```


```{r example CMP}
CMP.bids <- glm.CMP(formula.mu = numbids ~ leglrest + rearest + finrest +
                    whtknght + bidprem + insthold + size + size.sq +
                    regulatn,
                    formula.nu = numbids ~ 1,
                    data = Bids)
summary(CMP.bids)
AIC(CMP.bids)
BIC(CMP.bids)
coef(CMP.bids)
confint(CMP.bids)
head(fitted(CMP.bids))
head(residuals(CMP.bids))
```

